\documentclass[11pt]{article}
\setlength{\parindent}{0pt}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[utf8]{inputenc} 
\usepackage{ebgaramond}
\usepackage[T1]{fontenc}
\usepackage[left=0.75in,top=0.5in,right=0.75in,bottom=0.5in]{geometry}

\begin{document}
\pagestyle{empty}
\begin{center}
    \textbf{\Large Noah J. Case}\\ 

    \vspace{1pt}
    
    3815 14th St. NW, APT 2, Washington, DC 20011 \\ \href{mailto:noahcase119@gmail.com}{\texttt{noahcase119@gmail.com}} \textbullet \ +1 (860) 951-6829 \textbullet \ \url{www.linkedin.com/in/noahjcase}
\end{center}

\vspace{-20pt}
\hrulefill
\vspace{-6pt}

\begin{center}
    \textbf{EDUCATION} \\
\end{center}
\textbf{Vassar College,} \hfill Poughkeepsie, NY

\textit{Bachelor of Arts, Economics; Minor in Mathematics} \hfill May 2023
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item GPA: 3.88/4.00.
\end{itemize}

\begin{center}
    \textbf{WORK EXPERIENCE}
\end{center}

\textbf{Secretariat Economists} \textit{(formerly Economists Incorporated)}, \hfill Washington, DC

\textit{Associate} \hfill July 2023--Present
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Work directly with PhD economists to compile, clean, and analyze data relating to energy, healthcare, and insurance industries.
    \item Lead trainings for managers and other associates on topics such as Git, Stata data frames, and ETL processes and data management.
    \item Researched and helped draft a report on competition in the defense industry for the antitrust section of the American Bar Association long-range planning committee.
\end{itemize}

\vspace{12pt}

\textbf{Campuswire,} \hfill Remote

\textit{Microeconomics Teaching Assistant} \hfill September 2022--December 2022
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Led discussion section and hosted Office Hours. Graded assignments for fifteen students.
\end{itemize}
\vspace{12pt}

\textbf{Johns Hopkins University Center for Talented Youth,} \hfill Bristol, RI

\textit{Economics Teaching Assistant and Residential Program Assistant} \hfill June 2022--August 2022
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Worked with an instructor to teach an introductory Money and Banking course to rising 7th--10th graders. Primary instructor during evening sessions.
\end{itemize}

\vspace{12pt}

\textbf{Community Solutions,} \hfill Hartford, CT

\textit{Real Estate Data and Visualization Intern} \hfill June 2021--August 2021
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Surveyed more than 800 homes in the federally-designated North Hartford Promise Zone to assess blight conditions based on municipal blight ordinance, mapped survey results using ArcGIS.
    \item Developed process to track thirteen neighborhood metrics including foreclosures and rents.
\end{itemize}

\begin{center}
    \textbf{ACADEMIC PROJECTS}
\end{center}

\textbf{Undergraduate Thesis:} \textit{Land-Use Restrictions and Segregation: The Effect of Single-Family Zoning in Austin.}\\
\textbf{Research on Merger Pass-Through:} In-progress paper on merger pass-through in horizontally-consolidated industries with J\'essica Dutra (Secretariat). \\
\textbf{Research on Vertical Integration in Recreational Cannabis Industry:} Ongoing research assistance for paper by J\'essica Dutra, Panos Dimitrellos (Secretariat), and Greg Leung (CDC).




\begin{center}
    \textbf{AWARDS \& HONORS}
\end{center}

\textbf{Agnes Reynolds Jackson Prize:} Vassar Economics department prize for excellence in written work in Economics. \\
\textbf{Departmental Honors in Economics:} Honors awarded to approximately one quarter of majors. \\
\textbf{Premio Márquez:} Vassar Spanish department prize for nonfiction Spanish-language essay.\\
\textbf{Omicron Delta Epsilon:} International honor society in economics.

\begin{center}
    \textbf{SKILLS \& TEST SCORES}
\end{center}

\textbf{Technical:} Stata, R, Python, QGIS, ArcGIS, Git, \LaTeX, Excel, PDF Scraping.\\
\textbf{Language:} English (Native), Spanish (Intermediate proficiency).\\
\textbf{GRE Scores:} Verbal, 170 (99th percentile); Quantitative, 170 (92nd percentile); Analytical Writing, 6.0 (99th percentile).

\end{document}
